Estimating real-time high street footfall from Wi-Fi probe requests

### 2018-01-30 abstract.tex
update

>>>>

	We then use the fields - OUI, lengths and sequence number,
	to tackle the noise from devices which anonymising the probe requests.
	OUI and length are used to split the dataset into
	groups probe requests from similar
	devices and each subset is classified further
	based on a graph based clustering algorithm 
	where each cluster correspond to an unique device.
	The algorithm works by creating a graph where the nodes are the
	probe requests and the links are created between them based on the following
	rules,
	A link can go only forward in time.
	A link can exist between nodes with a 
		maximum time difference of t (time threshold)
	A link can go from low to high sequence numbers.
	A link can exist between nodes with a
		maximum sequence number difference of s (sequence threshold)
	A node can have only one incoming link and outgoing link
		which is the shortest of all possible such links.
	The nodes are then classified based on the unique connected component they
	belong to.
